draft

### 2025-06-30 draft.tex
fix(draft): replace — -> --
* draft.tex (subsection{Engineered features in the era of deep learning}):

Several practical considerations favour engineered features in biological imaging. 
First, interpretability remains crucial for biological discovery—researchers need to understand which morphological characteristics drive observed phenotypes. 
While deep learning features can be powerful predictors, their interpretation requires sophisticated techniques that may not provide the mechanistic insights biologists seek \citep{liChallengesOpportunitiesBioimage2023}. 
Engineered features have clear mathematical definitions that directly translate to biological concepts, such as protein co-localisation or nuclear morphology changes \cite{garcia-fossaInterpretingImagebasedProfiles2023}.

>>>>

Several practical considerations favour engineered features in biological imaging. 
First, interpretability remains crucial for biological discovery--researchers need to understand which morphological characteristics drive observed phenotypes. 
While deep learning features can be powerful predictors, their interpretation requires sophisticated techniques that may not provide the mechanistic insights biologists seek \citep{liChallengesOpportunitiesBioimage2023}. 
Engineered features have clear mathematical definitions that directly translate to biological concepts, such as protein co-localisation or nuclear morphology changes \cite{garcia-fossaInterpretingImagebasedProfiles2023}.
